Cosmological Evidences of Dark Matter through the CMB

### 2019-02-22 paper/main.tex
section 5.2

\section{Comments on the results and plots of the CMB spectrum}
The four density parameters $\Omega$ encode the energy-matter content of the Universe and they determine the evolution of space-time through the Friedmann equations. 
In section 4 we have outlined how we expect matter to behave at large and small scales.
We want now to link the information contained in the fluctuations of the CMB photons to the density parameters.\\
The behavior of the primordial plasma is imprinted in the CMB photons, in fact, we observe the density fluctuations as anisotropies in the sky map tempearature.
In order to relate the fluctuations at different scales and the deviations from the average temperature $2.7$ K on the CMB map, it is necessary to decompose the temperature deviation $T(\theta, \phi)$ into a set of orthonormal functions on the sky.
The spherical harmonics $Y^{m} _{l} (\theta, \phi)$ are suitable for this.\\
So if $T(\theta,\phi)$ is the temperature at position $(\theta,\phi)$ on the sky map,
we can write:
\begin{equation}
T(\theta, \phi) = \sum _{l, m} a_{lm} Y^{m} _l (\theta, \phi)
\end{equation}
Due to the orthonormality of the spherical harmonics, we obtain the coeaficients:
\begin{equation}
a_{lm} = \int _0 ^{2 \pi} \dd \phi \int _0  ^{\pi} \dd \theta \,
\sin( \theta) \, T(\theta, \phi) \, Y^{m} _l (\theta, \phi)
 \end{equation}
We define the power spectrum of the temperature map as 
 \begin{equation}
 C_l = \dfrac{1}{2l+1} \sum _{m=-l} ^{l} |a_{lm}|^2
 \end{equation}
Since $l \sim 1/ \theta$, for small $l$ we are considering big scales of the sky map, viceversa for big $l$.
As we consider increasing $l$ we are looking at fluctuations in the primordial plasma that have a decreasing  scale and thus wavelength.\\
The measured temperature power spectrum is shown in Figure(\ref{temp_pow_spect})
%
%
%
\begin{figure}
\includegraphics[width=0.9\textwidth]{planck2018}
\caption{Planck 2018 temperature power spectrum. $\mathcal{D}^{TT}_l = l(l+1)C_l$ (arXiv:1807.06209v1)}
\label{temp_pow_spect}
\end{figure}
%
%
%
For large scales, small $l<30$, the power spectrum is constant and oscillations do not take place.
Therefore, the Sachs-Wolfe effect is dominant on large scales where the oscillations have too large wavelength to complete an entire oscillations before recombination and they experience mainly the gravitational redshift.\\
For large $l$ the acoustic oscillations are dominant.
The first peak is at $l \approx 200$ approximately $1 ^o$ on the sky, it represents how the tiny variations in the fluid density gave rise to a sound wave which collapsed exactly at the time of recombination.
The position of the peak tells us at which scale the first total compression of the primordial plasma happened.
The second peak is linked to the maximal rarefaction of the plasma, so the position of the second peak tells us how the

The damping effect is evident for $l>10^{3}$.\\

>>>>

\section{Comments on the results and plots of the CMB spectrum}
The four density parameters $\Omega$ encode the energy-matter content of the Universe and they determine the evolution of space-time through the Friedmann equations. 
In section 4 we have outlined how we expect matter to behave at large and small scales.
We want now to link the information contained in the fluctuations of the CMB photons to the density parameters.\\
The behavior of the primordial plasma is imprinted in the CMB photons, in fact, we observe the density fluctuations as anisotropies in the sky map tempearature.
In order to relate the fluctuations at different scales and the deviations from the average temperature $2.7$ K on the CMB map, it is necessary to decompose the temperature deviation $T(\theta, \phi)$ into a set of orthonormal functions on the sky.
The spherical harmonics $Y^{m} _{l} (\theta, \phi)$ are suitable for this.\\
So if $T(\theta,\phi)$ is the temperature at position $(\theta,\phi)$ on the sky map,
we can write:
\begin{equation}
T(\theta, \phi) = \sum _{l, m} a_{lm} Y^{m} _l (\theta, \phi)
\end{equation}
Due to the orthonormality of the spherical harmonics, we obtain the coeaficients:
\begin{equation}
a_{lm} = \int _0 ^{2 \pi} \dd \phi \int _0  ^{\pi} \dd \theta \,
\sin( \theta) \, T(\theta, \phi) \, Y^{m} _l (\theta, \phi)
 \end{equation}
We define the power spectrum of the temperature map as 
 \begin{equation}
 C_l = \dfrac{1}{2l+1} \sum _{m=-l} ^{l} |a_{lm}|^2
 \end{equation}
Since $l \sim 1/ \theta$, for small $l$ we are considering big scales of the sky map, viceversa for big $l$.
As we consider increasing $l$ we are looking at fluctuations in the primordial plasma that have a decreasing  scale and thus wavelength.\\
The measured temperature power spectrum is shown in Figure(\ref{temp_pow_spect})
%
%
%
\begin{figure}
\centering
\includegraphics[width=0.9\textwidth]{planck2018}
\caption{Planck 2018 temperature power spectrum. $\mathcal{D}^{TT}_l = l(l+1)C_l$ (arXiv:1807.06209v1)}
\label{temp_pow_spect}
\end{figure}
%
%
%
For large scales, small $l<30$, the power spectrum is constant and oscillations do not take place.
Therefore, the Sachs-Wolfe effect is dominant on large scales where the oscillations have too large wavelength to complete an entire oscillations before recombination and they experience mainly the gravitational redshift.\\
For large $l$ the acoustic oscillations are dominant.
The first peak is at $l \approx 200$ approximately $1 ^o$ on the sky, it represents how the tiny variations in the fluid density gave rise to a sound wave which collapsed exactly at the time of recombination.
The position of the peak tells us at which scale the first total compression of the primordial plasma happened.
The second peak is linked to those oscillations that compressed and expanded, and they reached the maximal rarefaction of the plasma at recombinatio.
The third peak is related to the oscillations that collapsed expanded and recollapsed, and so on for the higher peaks.\\
Notice that as we consider higher and higher $l$, i.e. smaller scales, the damping effects become relevant, especially for  $l>10^{3}$.
